Robustly decorrelating errors with mixed quantum gates

### 2020-05-08 decorrelation/mixed_unitaries.tex
final update before resubmitting

The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Eq.~\eqref{eq:minimization}:
\begin{equation}\label{eq:minimization_sparsity}
\begin{split}
&\underset{m\in[1..N]}{\textbf{minimize:}}\\
&\ \ \bunderbrace{\textbf{\hspace{.2cm}minimize:\hspace{.2cm}} }{\hspace{.1cm}\weight_i\geq0, |\weight|_1=1, t\geq0} ||\mathbf{L}\cdot\vec\weight||_2 + t\\
&\ \ \hspace{.2cm}\textbf{subject to: } \weight_m > \frac{\lambda}{t}.
\end{split}
\end{equation}
Here, $\lambda \geq 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution. If $\lambda$ is set to zero, the inner program reduces to Eq.~\eqref{eq:minimization} and the outer minimization is redundant. If $\lambda$ is very large each inner minimization problem is minimized for an MQG with a single control, and the outer minimization simply selects the control which has the error generator of smallest norm. While this gives a maximally sparse solution, it doesn't allow for any cancellation of coherent errors. In particular, increasing $\lambda$ will increase the sparsity of the solution, but will generally decrease the likelihood that the solution will be generator-exact.

>>>>

The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Eq.~\eqref{eq:minimization}:
\begin{equation}\label{eq:minimization_sparsity}
\begin{split}
&\underset{m\in[1..N]}{\textbf{minimize:}}\\
&\ \ \bunderbrace{\textbf{\hspace{.2cm}minimize:\hspace{.2cm}} }{\hspace{.1cm}\weight_i\geq0, |\weight|_1=1, t\geq0} ||\mathbf{L}\cdot\vec\weight||_2 + t\\
&\ \ \hspace{.2cm}\textbf{subject to: } \weight_m > \frac{\lambda}{t}.
\end{split}
\end{equation}
Here, $\lambda \geq 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution. If $\lambda$ is set to zero, the inner program reduces to Eq.~\eqref{eq:minimization} and the outer minimization is redundant. If $\lambda$ is very large, each inner minimization problem is minimized for an MQG with a single control, and the outer minimization simply selects the control which has the error generator of smallest norm. While this gives a maximally sparse solution, it doesn't allow for any cancellation of coherent errors.

In general, increasing $\lambda$ decreases the number of controls with large weights, and by removing controls with weights below a threshold probability we can increase the sparsity of the solution. Truncating in this way will introduce error in the Pauli-exactness of the solution. For larger $\lambda$ the required threshold probability decreases, and so the error introduced from truncation can be made smaller. However, larger $\lambda$ will also decrease the likelihood of the optimizer returning a generator-exact solution, and so in this way, tuning $\lambda$ allows us to trade between different sources of error when constructing sparse MQGs.
